WHOOMP! (There It Is) \\ Rapid Bayesian position reconstruction for gravitational\nobreakdashes-wave transients

### 2015-07-08 ms.tex
Add some acknowledgements

@@

This research is supported by the \ac{NSF} through a Graduate Research Fellowship to L.S.

L.S. thanks the Aspen Center for Physics and \ac{NSF} Grant \#1066293 for hospitality during the editing of this paper.

Source code for \ac{BAYESTAR} is available as part of LALInference, the open source LIGO/Virgo parameter estimation toolchain. See \url{http://www.lsc-group.phys.uwm.edu/daswg/projects/lalsuite.html} for further details.

Some of the results in this paper have been derived using \ac{HEALPix} \cite{healpix}.

@@

We thank Britt Griswold for assistance with preparing Figure~\ref{fig:adaptive-illustration}.
\end{acknowledgements}

>>>>

We thank John Veitch and Will Farr for chairing a review of the analysis and code. We thank Britt Griswold for assistance with preparing Figure~\ref{fig:adaptive-illustration}.
\end{acknowledgements}

@@

This research was supported by the \ac{NSF} through a Graduate Research Fellowship to L.S. L.S. thanks the Aspen Center for Physics and \ac{NSF} Grant \#1066293 for hospitality during the editing of this paper.

Source code for \ac{BAYESTAR} is available as part of LALInference\footnote{\url{https://ligo-vcs.phys.uwm.edu/cgit/lalsuite/tree/lalinference}}, the open source LIGO/Virgo parameter estimation toolchain, which is in turn part of LALSuite\footnote{\url{http://www.lsc-group.phys.uwm.edu/daswg/projects/lalsuite.html}}. This research made use of Astropy\footnote{\url{http://www.astropy.org}} \citep{astropy}, a community-developed core Python package for astronomy. Some of the results in this paper have been derived using \ac{HEALPix}\footnote{\url{http://healpix.sourceforge.net}} \cite{healpix}.

@@
